%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\definecolor{MyBlue}{HTML}{187cb5}
%\definecolor{Myblue}{rgb}{0.0,0.0,0.0}
%---------------------------------------------------------
  

%---------------------------------------------------------
  \cventry
    {Personal Project} % Job title
    {Raspberry Pi Motion Detection Alarm System} % Organization
    {}% Location
    {\textcolor{MyBlue}{Python}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A motion activated alarm with network connectivity using a Raspberry Pi 2 model B, an infrared motion detector, a buzzer alarm, and a Netgear Nighthawk R7000 router.}
        \item {Raspbian was installed on the Raspberry Pi as the base operating system. The Gpiozero Python library was used as an interface to the motion detector and buzzer alarm, which were connected to the GPIO pins of the Raspberry PI. }
        \item {The Python Socket library was used to write a network class that served as the interface for communicating with other devices on the network. The goal of this project was to create a motion sensor that would serve as one component to a larger home security system.}
        \end{cvitems}
    }
    
%---------------------------------------------------------
 
%---------------------------------------------------------

\cventry
    {Freelance} % Job title
    {Automated Trading} % Organization
    {} % Location
    {\textcolor{MyBlue}{Flask, Heroku, Robinhood API, Python}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item{Created A Flask app using python and Heruko to execute stock market trades.}
        \item {Created a pine script to detect entry and exit points using bollinger band breakouts and additional indicators. } 
        \item{Using Webhooks from TradingView.com JSON post requests for buy and sell signals where sent to the Flask APP using request libraries}
        \item {The information was then used with Robinhood api to execute trades}
      \end{cvitems}
    }

%---------------------------------------------------------
 
%---------------------------------------------------------
%\definecolor{MyBlue}{HTML}{187cb5}

  \cventry
    {Side Project} % Job title
    {Gender Predictions with Neural Networks} % Organization
    {} % Location
    {\textcolor{MyBlue}{Python, Numpy, Beautifulsoup}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a two layer neural network from scratch using python and numpy to classify gender based on weight and height data}
        \item {Achieved 94.8\% accuracy on the 1000 epoch}
        \item {Created weight and height data sets by web scraping the CDC National Health Statics Report 1990-2000 through 2015-2016 using Beautifulsoup}
      \end{cvitems}
    }
   
%---------------------------------------------------------
 
%---------------------------------------------------------


    
%---------------------------------------------------------
 
%---------------------------------------------------------

  \cventry
    {Side Project} % Job title
    {Pathfinding Algorithm Visualizer} % Organization
    {} % Location
    {\textcolor{MyBlue}{Python, Pygame}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented A*, Depth-first and Breadth-first searching algorithms in Python and designed a path-finding visualizer tool using the Pygame library}
        \item {Conceptualized the efficiency of informed search algorithms versus uniformed search algorithms}
      \end{cvitems}
    }

%---------------------------------------------------------
 
%---------------------------------------------------------
  \cventry
    {Colorado State University} % Job title
    {Operations} % Organization
    {Fort Collins, CO} % Location
    {Oct. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Plan and coordinate tasks to maintain building operations at the Lory Student Center}
        \item {Instrumental in leading teams to implement new public health orders}
        \item{Advise and train new incoming students workers}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
